
```{r}
load(url("https://github.com/zhentaoshi/Econ5821/raw/main/data_example/dataset_inf.Rdata"))
X_colnames <- read.csv("https://github.com/zhentaoshi/Econ5821/raw/main/data_example/X_colnames.csv")
colnames(X) = paste0("x", X_colnames$X)
```
# Calculate the inflation rate
```{r}
# Generate a null vector
n <- nrow(cpi)
inf=vector("numeric", length = n-12)

# Calculate the inflation rate
for (i in 1:(n-12)) {
  p1 = i+12
  p2 = i
  inf[i] <- (log(cpi[p1,2])-log(cpi[p2,2]))
}
inf <- as.data.frame(inf, col.names = "inf")
inf <- t(inf)
colnames(inf)[1] <- "INF"
```
# Use mutate() and cross() functions to convert all variables in X to numeric, check for missing values
```{r}
library(dplyr)
X <- X %>% mutate(across(everything(), as.numeric))
X[is.na(X)] <- 0
X[, sapply(X, is.factor)] <- lapply(X[, sapply(X, is.factor)], as.numeric)
```
# Delete the first 12 rows of X and merge the data
```{r}
X <- X[-(1:12), ]
data <- cbind(inf, X)
```
# Divide the dataset into training and test sets + # Handle missing values and normalization
```{r}
train_size <- floor(0.8 * nrow(data))
train <- data[1:train_size, ]
test <- data[(train_size + 1):nrow(data), ]

train[, -2] <- scale(train[, -2]) # Normalized time series and variables other than inf
train[is.na(train)] <- 0 
test[, -2] <- scale(test[, -2])
test[is.na(test)] <- 0
```
#lasso:Fitting the LASSO regression model using all columns in the training set (except the month column) as independent variables and using the inf column in the training set as the dependent variable:
```{r}
library(glmnet)
x_train <- as.matrix(train[, -(1:2)]) # Select all columns except the first two as independent variables
y_train <- train$INF
lasso_model <- glmnet(x_train, y_train, alpha = 1)

# Select the best regularization parameter lambda using the cross-validation method:
cv_model <- cv.glmnet(x_train, y_train, alpha = 1, nfolds = 10, type.measure = "mse")
best_lambda <- cv_model$lambda.min

# Fit the LASSO model using the best regularization parameter lambda
lasso_model <- glmnet(x_train, y_train, alpha = 1, lambda = best_lambda)
```

```{r}
# Predictions on the test set
x_test <- as.matrix(test[, -(1:2)])
y_test <- test$INF
y_pred <- predict(lasso_model, newx = x_test)

# Calculate MSE and MAE, R-squared
mse <- mean((y_test - y_pred)^2)
mae <- mean(abs(y_test - y_pred))
r2 <- 1 - sum((y_test - y_pred)^2) / sum((y_test - mean(y_test))^2)
```

